\plaintitle

### 2017-01-10 drafts/labor/relationships.tex
chinmay's suggestions integrated

% \onlyinsubfile{\clearpage}
\subsubsection{\crowdworkpers}
\begin{comment}
	- Workers do it for money
	- Workers coordinate and communicate (gray, being a turker, team stuff). there is mega-drama
	- Workers don't like requesters. have tried to organize
\end{comment}

@@

% \onlyinsubfile{\clearpage}
\subsubsection{\pieceworkpers}

@@

\topic{Early observers believed that workers were strongly motivated by the autonomy of working in the piecework model}.
\citeauthor{clark1908cotton} observed textile mill pieceworkers and reported,
``When he works by the day the Italian operative wishes to leave before the whistle blows,
but if he works by the piece he will work as many hours as it is possible for him to stand.''
However, the emergent trend contrasted with this early rhetoric, as
when workers began instituting ``The Fix'', deliberately slow work to game efficiency experts~\cite{roy1954efficiency}.
Piece workers, \citeauthor{roy1954efficiency} found, would form even more starkly antagonistic relationships with their managers.
% Workers' situations were quite dire: \citeauthor{riisOtherSideLives}  documented abhorrent working and living conditions of pieceworkers in New York City~\cite{riisOtherSideLives}.

@@

\topic{Relative to the modern on--demand workers, there is a noticeable dearth of information on the inter--personal relationships among pieceworkers
beyond the match--girls at the end of the \nth{19} century.}
% For one thing, the research methods we typically associate with the exploratory study of cultures
% --- Anthropology, and namely participant--observation, ethnography, etc\dots~---
% didn't exist quite as we know them at the turn of the \nth{20} century, and wouldn't for several more decades.
Nevertheless, we can offer some observations:
primary sources indicate that labor organizations wished for workers to identify as a collective group, 
``not only as railroad employees but also as members of the larger life of the community''~\cite{american1921problem}.
Doing this, 
\citeauthor{ostrom1990governing} and others later argued,
would facilitate collective action and perhaps collective governance~\cite{ostrom1990governing,russell1982collective,olsonlogic}.
\citeauthor{riisOtherSideLives} also contributed to this sense of shared struggle and endurance
by documenting pieceworkers in their home--workplaces,
literally bringing to light the grim circumstances in which pieceworkers lived and worked~\cite{riisOtherSideLives}.

% \onlyinsubfile{\clearpage}
\subsubsection{\whatchanged}

@@

%While historical pieceworkers could be looked down on, as the match-stick girls were characterized by ``brashness, irregularity, low morality, and little education'', 
There was generally less written about work quality concerns for historical pieceworkers than there is in modern on--demand work. 
Why the difference? 
One possibility is that, through writing web scripts and applying them to many tasks, it is possible for a small number of spammers have an outsized influence.
Another possibility: it was much harder for piece workers to move to a new location and get a new job --- today, workers can simply accept a different task on Mechanical Turk.
A third possibility: online anonymity breeds distrust~\cite{friedman2000trust}, and where pieceworkers could be directly observed by foremen and known to them, online workers are known by little more than an account ID.

\topic{The relationship between workers and employers has also shifted: while historically the management of workers had to be done through a foreman
(who necessarily had an intuitive
--- perhaps sympathetic ---
relationship with workers),
the foreman of the \nth{20} century has largely been replaced
by algorithms of the \nth{21} century~\cite{uberAlgorithm}.}
The result of this change is that the agents managing work are now
cold, logical, and unforgiving.
Where a person might recognize that the ``attention check'' questions 
proposed by \citeauthor{le2010ensuring} ensure that malicious and inattentive workers are stopped,
some implementations of these approaches
only seem to antagonize workers.
More than 30 years ago, \citeauthor{10.2307/2555446} wrote:
``When performance is difficult to evaluate,
imperfect input measures and
a manager's subjective judgment are preferable to
defective (simple, observable) output measures''~\cite{10.2307/2555446}.
This frustration has only grown as requesters have had to rely on automatic management mechanisms. Only a few use the equivalent of human foremen~\cite{haas2015argonaut,kulkarni2012mobileworks}.

@@

% \onlyinsubfile{\clearpage}
\subsubsection{\implication}

The decentralization and anonymization of on--demand work, especially online crowd work, will continue to make many of its social relationships a struggle.
While some workers get to know each other well on forums~\cite{martin2014being,crowdcollab}, many never engage in these social spaces.
Without intervention, worker relationships and collectivism are likely to be inhibited by this decentralized design.
One option is to build worker centralizing points into the platform, for example asking workers to vote on each others' reputation or allowing groups of workers to collectively reject a task from the platform~\cite{crowdguilds}.

@@

\topic{Reciprocally, crowd work may be able to inform piecework research in this domain.}
There exists far less literature about piece workers' relationships than there does today about on--demand workers' relationships.
Two reasons stand out: first, modern platforms are visible to researchers in ways that the sites of piece work labor were not.
Second, Anthropology stands on a firmer theoretical and methodological basis than it did at the turn of the \nth{20} century.
\citeauthor{malinowski2002argonauts,boas1940race,mead1973coming} and
other luminaries throughout the first half of the \nth{20} century
effectively defined Cultural Anthropology as we know it today;
\textit{participant--observation},
the \textit{etic} and the \textit{emic} understanding of culture, and
\textit{reflexivity}
didn't take even a resemblance of their contemporary forms until these works~\cite{malinowski2002argonauts,boas1940race,mead1973coming}.
On--demand labor today may give us an opportunity to revisit open questions in piecework with a more refined lens.

>>>>

\subsubsection{\crowdworkpers}
\begin{comment}
	- Workers do it for money
	- Workers coordinate and communicate (gray, being a turker, team stuff). there is mega-drama
	- Workers don't like requesters. have tried to organize
\end{comment}

@@

\subsubsection{\pieceworkpers}

@@

\topic{Early observers believed that workers were strongly motivated by the autonomy of working in the piecework model}.
\citeauthor{clark1908cotton} observed textile mill pieceworkers and reported,
``When he works by the day the Italian operative wishes to leave before the whistle blows,
but if he works by the piece he will work as many hours as it is possible for him to stand.''
However, the emergent trend contrasted with this early rhetoric, as
when workers began instituting ``The Fix'', deliberately slow work to game efficiency experts~\cite{roy1954efficiency}.
Piece workers, \citeauthor{roy1954efficiency} found, would form even more starkly antagonistic relationships with their managers.

@@

\topic{Relative to the modern on--demand workers, there is a noticeable dearth of information on the inter--personal relationships among pieceworkers
beyond the match--girls at the end of the \nth{19} century.}
Nevertheless, we can offer some observations:
primary sources indicate that labor organizations wished for workers to identify as a collective group, 
``not only as railroad employees but also as members of the larger life of the community''~\cite{american1921problem}.
Doing this, 
\citeauthor{ostrom1990governing} and others later argued,
would facilitate collective action and perhaps collective governance~\cite{ostrom1990governing,russell1982collective,olsonlogic}.
\citeauthor{riisOtherSideLives} also contributed to this sense of shared struggle and endurance
by documenting pieceworkers in their home--workplaces,
literally bringing to light the grim circumstances in which pieceworkers lived and worked~\cite{riisOtherSideLives}.

\subsubsection{\whatchanged}

@@

There was generally less written about work quality concerns for historical pieceworkers than there is in modern on--demand work. 
Why the difference? 
One possibility is that, through writing web scripts and applying them to many tasks, it is possible for a small number of spammers have an outsized influence.
Another possibility: it was much harder for piece workers to move to a new location and get a new job --- today, workers can simply accept a different task on Mechanical Turk.
A third possibility: online anonymity breeds distrust~\cite{friedman2000trust}, and where pieceworkers could be directly observed by foremen and known to them, online workers are known by little more than an account ID.

\topic{The relationship between workers and employers has also shifted: while historically the management of workers had to be done through a foreman
(who necessarily had an intuitive
--- perhaps sympathetic ---
relationship with workers),
the foreman of the \nth{20} century has largely been replaced
by algorithms of the \nth{21} century~\cite{uberAlgorithm}.}
The result of this change is that the agents managing work are now
cold, logical, and unforgiving.
Where a person might recognize that the ``attention check'' questions
proposed by \citeauthor{le2010ensuring} and others ensure that
malicious and inattentive workers are stopped~\cite{le2010ensuring,AAAIW113995},
some implementations of these approaches
only seem to antagonize workers~\cite{takingAHITMcInnis}.
More than 30 years ago, \citeauthor{10.2307/2555446} wrote:
``When performance is difficult to evaluate,
imperfect input measures and
a manager's subjective judgment are preferable to
defective (simple, observable) output measures''~\cite{10.2307/2555446}.
This frustration has only grown as requesters have had to rely on automatic management mechanisms. Only a few use the equivalent of human foremen~\cite{haas2015argonaut,kulkarni2012mobileworks}.

@@

\subsubsection{\implication}
The decentralization and anonymization of on--demand work, especially online crowd work, will continue to make many of its social relationships a struggle.
While some workers get to know each other well on forums~\cite{martin2014being,crowdcollab}, many never engage in these social spaces.
Without intervention, worker relationships and collectivism are likely to be inhibited by this decentralized design.
One option is to build worker centralizing points into the platform, for example asking workers to vote on each others' reputation or allowing groups of workers to collectively reject a task from the platform~\cite{crowdguilds}.

@@

\topic{Reciprocally, crowd work may be able to inform piecework research in this domain.}
There exists far less literature about piece workers' relationships than there does today about on--demand workers' relationships.
Two reasons stand out: first, modern platforms are visible to researchers in ways that the sites of piece work labor were not.
Second, Anthropology stands on a firmer theoretical and methodological basis than it did at the turn of the \nth{20} century.
Malinowski, Boas, Mead, and
% \citeauthor{malinowski2002argonauts,boas1940race,mead1973coming} and % this was naming Boas twice, so.
other luminaries throughout the first half of the \nth{20} century
effectively defined Cultural Anthropology as we know it today;
\textit{participant--observation},
the \textit{etic} and the \textit{emic} understanding of culture, and
\textit{reflexivity}
didn't take even a resemblance of their contemporary forms until these works~\cite{malinowski2002argonauts,boas1940race,mead1973coming}.
On--demand labor today may give us an opportunity to revisit open questions in piecework with a more refined lens.
